Missing The Point:

### 2020-07-15 ICML/MissingThePoint.Rmd
Save pdf version of presentation

---
title: "Missing The Point:"
subtitle: "Non-Convergence in Iterative Imputation Algorithms"
author: "Hanne I. Oberman, Stef van Buuren, Gerko Vink"
institute: "ICML ARTEMISS workshop 2020"
date: "17-07-2020" #(updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    #seal: false
    self_contained: true
    css: [default, default-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

@@

.pull-right[
<img src="https://raw.githubusercontent.com/gerkovink/shinyMice/2dae400d9d23ede7bec031c1501acdc681eab13c/ThesisProposal/Figures/logo.png" width="595">
]
]
<!-- .footnote[Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).] -->

>>>>

---
title: "Missing The Point:"
subtitle: "Non-Convergence in Iterative Imputation Algorithms"
author: "Hanne I. Oberman, Stef van Buuren, Gerko Vink"
institute: "ICML ARTEMISS workshop 2020"
date: "17-07-2020" #(updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    seal: false
    self_contained: true
    css: [default, default-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

@@

.pull-right[
<img src="https://github.com/gerkovink/shinyMice/blob/edits/ICML/shinymicehex.png?raw=true" width="255">
]
]
<!-- .footnote[Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).] -->
